
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Science Consultant} % Job title
    {Logos News, LLC} % Organization
    {Los Angeles, CA} % Location
    {April 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Extracted and processed over one million different types of data (numeric, textual) in Python from several news media sources by utilizing developer APIs.}
        \item {Built a Comment-Ranking Model, a model that quantifies the quality of a comment by predicting the: toxicity, subjectivity, political affiliation, and quality of a comment.}  
        \vspace{4mm}
        \begin{cvitems}
        	\item {Utilized Natural Language Processing packages in Python (Keras, Tensorflow) to pre-process textual data and transform words into vectors using Word2Vec.}
        	\item {Yielded over 90\% successful classification rate by applying a neural network algorithm called Long Short-Term Memory model to training and testing data.}
        \end{cvitems}
        \vspace{4mm}
        \item {Led the development of the User Reputation Model project, a project aimed to increase consumer experience and satisfaction on the app by calculating a user’s reputation score for app personalization purposes.}
        \vspace{4mm}
        \begin{cvitems}
        	\item {Employed project management skills to coordinate project tasks. Researched appropriate methods to gather information in order to develop project scope, and conduct work plans. Provided status updates to management frequently.}
        \end{cvitems}
    	\vspace{4mm}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Ornus Capital, LLC} % Organization
    {Los Angeles, CA} % Location
    {April 2019 - June 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Found and optimized a portfolio of assets, which outperformed the market by over 30\%.}
        \vspace{4mm}
        \begin{cvitems}
        	\item {Applied portfolio theory (e.g. Markowitz theory), regression analysis, and bootstrap/simulation methods in order to find portfolios with highest expected returns, and portfolios with lowest risks (minimum variance).}
        \end{cvitems}
   		\vspace{4mm}
        \item {Automated a program in Python that extracts, translates, and loads historical data of user-inputted cryptocurrencies within a specific time period.}
        \vspace{4mm}
        \begin{cvitems}
        	\item {This program automatically outputs a heatmap of the correlation coefficients, time-series plots, and scatterplots with fitted OLS regression lines in order to get a better understanding of asset and variable relationships, and to identify trends and correlations.}
        \end{cvitems}
    	\vspace{4mm}	
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Analyst Intern} % Job title
    {Clayton Treat Automotives} % Organization
    {Concord, CA} % Location
    {June 2018 - September 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Increased labor work and revenue by over 10\% by conducting local market research and statistical analysis.}
        \vspace{4mm}
        \begin{cvitems}
        	\item{Performed time-series analysis in Microsoft Excel to determine which types of jobs combined with time periods generated most revenue.}
        	\item {Suggested and implemented recommendations, which included: creating promotional offers during certain time periods with lagging sales, changing price tags of many car parts and labor costs, implementing workflow solutions and process improvement opportunities, and more.}
        \end{cvitems}
    	\vspace{4mm}
        \item {Assisted in the creation of a business website and placed promotional offers on there.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
